Working title: Ecological network control

### 2018-06-08 paper/manuscript.Rmd
Initial commit of results
Addresses #19

>>>>

# Results

```{r controllability}
drake::loadd(controllability, metadata)
c_m <- controllability %>% 
  filter_networks_df(metadata)
```

The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between `r round(min(c_m$n_D), 2)` and `r round(max(c_m$n_D), 2)` (mean `r round(mean(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)).

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/sqrt(2), fig.cap="Density plot ofsize of the minimum driver node set. The vertical dashed line indicates the meann value."}
drake::loadd(fig_emp_controllability)
fig_emp_controllability
```
